An Elastica-driven Digital Curve Evolution Model for Image Segmentation\thanks{This work has been partially funded by CoMeDiC ANR-15-CE40-0006 research grant.}

### 2020-05-20 Revision/R1_latex/manuscript.tex
Replace long filenames to shorter ones

\begin{figure}
\center
\includegraphics[scale=0.5]{optimization_pairwise-ratio_plot-pairwiseratio-lowerHigher-concavities-probe.pdf}
\caption{We plot the ratio of pairwise terms among all $\binom{|X^{(i)}|}{2}$ combinations. The highest ring has roughly half the number of pairwise terms as the lowest ring.}
\label{fig:ratio-pairwise-terms}
\end{figure}

\begin{figure}[]
\center
\begin{minipage}[b]{0.5\textwidth}
\subfloat[]{ \includegraphics[scale=0.35]{optimization_unlabeled-iterations_radius-3_plot-model-square-concavities-probe.pdf}}\\%
\subfloat[]{ \includegraphics[scale=0.35]{optimization_unlabeled-iterations_radius-5_plot-model-square-concavities-probe.pdf}}\\%
\subfloat[]{ \includegraphics[scale=0.35]{optimization_unlabeled-iterations_radius-7_plot-model-square-concavities-probe.pdf}}%
\end{minipage}%
\begin{minipage}[b]{0.5\textwidth}
\subfloat[]{ \includegraphics[scale=0.35]{optimization_unlabeled-iterations_radius-3_plot-model-flower-concavities-probe.pdf}}\\%
\subfloat[]{ \includegraphics[scale=0.35]{optimization_unlabeled-iterations_radius-5_plot-model-flower-concavities-probe.pdf}}\\%
\subfloat[]{ \includegraphics[scale=0.35]{optimization_unlabeled-iterations_radius-7_plot-model-flower-concavities-probe.pdf}}%
\end{minipage}
\caption{For each plot, we first produce shapes $\left\{ S^{(i)} \right\}$ executing DCE with $m=r$. Then, for each shape in $\left\{ S^{(i)} \right\}$, we execute one iteration of DCE for different values of $m$ and we count the unlabeled pixels. The number of unlabeled pixels by QPBOP remains high for lower values of $m$, and goes to zero when $m=r$. We observe the same behaviour for varying radius values.}
\label{fig:unlabeled-versus-iterations}
\end{figure}

>>>>

\begin{figure}
\center
\includegraphics[scale=0.5]{opt_pairwise_ratio_concavities_probe.pdf}
\caption{We plot the ratio of pairwise terms among all $\binom{|X^{(i)}|}{2}$ combinations. The highest ring has roughly half the number of pairwise terms as the lowest ring.}
\label{fig:ratio-pairwise-terms}
\end{figure}

\begin{figure}[]
\center
\begin{minipage}[b]{0.5\textwidth}
\subfloat[]{ \includegraphics[scale=0.35]{opt_unlabeled_it_r3_square_concavities_probe.pdf}}\\%
\subfloat[]{ \includegraphics[scale=0.35]{opt_unlabeled_it_r5_square_concavities_probe.pdf}}\\%
\subfloat[]{ \includegraphics[scale=0.35]{opt_unlabeled_it_r7_square_concavities_probe.pdf}}%
\end{minipage}%
\begin{minipage}[b]{0.5\textwidth}
\subfloat[]{ \includegraphics[scale=0.35]{opt_unlabeled_it_r3_flower_concavities_probe.pdf}}\\%
\subfloat[]{ \includegraphics[scale=0.35]{opt_unlabeled_it_r5_flower_concavities_probe.pdf}}\\%
\subfloat[]{ \includegraphics[scale=0.35]{opt_unlabeled_it_r7_flower_concavities_probe.pdf}}%
\end{minipage}
\caption{For each plot, we first produce shapes $\left\{ S^{(i)} \right\}$ executing DCE with $m=r$. Then, for each shape in $\left\{ S^{(i)} \right\}$, we execute one iteration of DCE for different values of $m$ and we count the unlabeled pixels. The number of unlabeled pixels by QPBOP remains high for lower values of $m$, and goes to zero when $m=r$. We observe the same behaviour for varying radius values.}
\label{fig:unlabeled-versus-iterations}
\end{figure}
